Trajipaq_sentiment_cr

### 2023-08-10 1. Trajipaq_sentiment/2. Codes/Trajipaq_sentiment_cr.Rmd
WGI update

Trajipaq_sentiment_cr <-
  trajipaq %>%
  select("age", # Création de la base de données dédiée à l'analyse.
         "education",
         "sexe",
         "annee_qc",
         "origine",
         "revenu",
         "langue_mat",
         "religion",
         "statut_mat",
         "Q11",
         "sentimapp_QC",
         "sentimapp_can_dico",
         "sentimapp_can_long",
         "sentimapp_origine_dico",
         "sentimapp_can_origine",
         "discrim_score",
         "vae_arrival",
         "pve_arrival",
         "gee_arrival",
         "rqe_arrival",
         "rle_arrival",
         "cce_arrival",
         "vae_2021",
         "pve_2021",
         "gee_2021",
         "rqe_2021",
         "rle_2021",
         "cce_2021",
         "vae_can",
         "pve_can",
         "gee_can",
         "rqe_can",
         "rle_can",
         "cce_can",
         "vae_arrival_diff",
         "pve_arrival_diff",
         "gee_arrival_diff",
         "rqe_arrival_diff",
         "rle_arrival_diff",
         "cce_arrival_diff"

         )

>>>>

Trajipaq_sentiment_cr <-
  trajipaq %>%
  select("age", # Création de la base de données dédiée à l'analyse.
         "education",
         "sexe",
         "annee_qc",
         "origine",
         "revenu",
         "langue_mat",
         "religion",
         "statut_mat",
         "Q11",
         "sentimapp_QC",
         "sentimapp_can_dico",
         "sentimapp_can_long",
         "sentimapp_origine_dico",
         "sentimapp_can_origine",
         "discrim_score",
         "vae_arrival",
         "pve_arrival",
         "gee_arrival",
         "rqe_arrival",
         "rle_arrival",
         "cce_arrival",
         "vae_2021",
         "pve_2021",
         "gee_2021",
         "rqe_2021",
         "rle_2021",
         "cce_2021",
         "vae_can",
         "pve_can",
         "gee_can",
         "rqe_can",
         "rle_can",
         "cce_can",
         "vae_arrival_diff",
         "pve_arrival_diff",
         "gee_arrival_diff",
         "rqe_arrival_diff",
         "rle_arrival_diff",
         "cce_arrival_diff"
         )
